How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-30 tse-paper/content.tex
Add new figure and text for lit survey

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/lit-sur/use.pdf}
		\caption{Purpose of build log analysis.}
		\label{fig:litsur:use}

@@

In this section, we describe what sort of information the articles in
our survey usually retrieved from build logs.
These results are depicted in \Cref{fig:litsur_r}.

@@

% TODO Moritz: add missing figure
% C: this (to be 4b) is closer to 4a, therefore I moved it up
% and the use/purpose down (to be 4c then)
We also identified the type of information which the articles
retrieved from the build logs.
In most cases (51\%), the researchers retrieved a chunk of text.
They scanned build logs for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, they distinguish failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
determine whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

\Cref{fig:litsur:use} shows the reason for the
investigated articles to analyze build logs.
The majority of articles (46\%) used the outcome of their build log
analysis to drive further research.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other articles (10\%) used the gained insights to give feedback to
developers.
For 8\% of the articles the retrieved information was the input
to a next automatic onward processing step:
articles chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

>>>>

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/lit-sur/kind.pdf}
		\caption{Class of information analyzed.}
		\label{fig:litsur:kind}

\end{subfigure}
\begin{subfigure}[t]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/lit-sur/use.pdf}
		\caption{Purpose of build log analysis.}
		\label{fig:litsur:use}

@@

In this section, we describe what sort of information the articles in
our survey usually retrieved from build logs.
\Cref{fig:litsur_r} depicts these results.

@@

\Cref{fig:litsur:kind} depicts that there are two widely used ways to
extract information from build logs: either chunks (53\%) or
classifications (41\%).
Uses for chunks were extracting compilation errors,
test failures, or the duration of build
tasks~\cite{clemencic2014new,zhang2016android}.
Examples for
classifications were distinguishing failures caused by developers from
failures caused by infrastructure errors~\cite{lindqvist2019detection}
or determining whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Categorization is the more abstract representation, chunks
contain more information and could be turned into a categorization.

\Cref{fig:litsur:use} shows the reason for the
investigated articles to analyze build logs, and the result also explains
the prevalence of classification.
The majority of articles (46\%) used the outcome of their build log
analysis to drive further research---and it is science aims to try to
classify and abstract.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other articles (10\%) used the gained insights to give feedback to
developers.
For 8\% of the articles the retrieved information was the input
to a next automatic onward processing step:
articles chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.
